---
title: "Slides in the classroom"
author: "Put your name here"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
# output: beamer_presentation #basic Presentation style
output:
  beamer_presentation:
  # https://hartwork.org/beamer-theme-matrix/ Source theme grid
    theme: "madrid"
    # colortheme: "dolphin"
    fonttheme: "serif" #structurebold

keep-tex: no
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


## Statistics to compute

1. Mean
1. Standard deviation
1. Variance
1. Range
1. Max and Min

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
mcar <- mean(cars$speed)
```

### Using calculated values in the slides.

The mean of the the Speed column is `r mcar`.

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Equations

$$
s^2 = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}
$$

## Equations II

### Create an aligned equation environment
\begin{align}
s^2 & = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}\\
s^2 & = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}\\
s^2 & = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}
\end{align}

## Including comments

$$
\begin{aligned}
    3+x &=4 && \text{(Solve for } x.)\\
    x &=4-3 && \text{(Subtract 3 from both sides.)}\\
    x &=1   && \text{(Solution.)}
\end{aligned}
$$

\structure{Answers}
Rather easy to create these


## Creating Tables

Col1       Col2              Col3
------    ----------    ---------
January    Free          Day
February   Reel          Fish
March      Hotness       Cold^[Very]
------    ----------    ---------

Table: My Dataset

Included a footnote here...

---- 
<!--Creates a plain slide quickly. -->
### Plain slide. 

Great for full page graphics etc.
