---
title: "Slides in the classroom"
author: "Put your name here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
    logo: vt.jpg
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Changing font sizes?. (title) | Yes, we can do it. (subtitle)

`<font size="xxx"> Blurb!</font>`

- <font size="1"> Blurb!</font>
- <font size="2"> Blurb!</font>
- <font size="3"> Blurb!</font>
- <font size="4"> Blurb!</font>
- <font size="5"> Blurb!</font>

## Controls | Good to know

The following single character keyboard shortcuts enable alternate display modes:

- 'f' enable fullscreen mode

- 'w' toggle widescreen mode

- 'o' enable overview mode

- 'h' enable code highlight mode

- 'p' show presenter notes


### Here's texts
<div class="red2">
This text is some red text!
</div>


## Slide with Bullets|Speaker's Notes added {.build} 

Content will be displayed incrementally using the `{.build}` funcion. 

For example:

- Bullet 1
- Bullet 2
- Bullet 3

<div class="notes">
This is my *note*.

- I need to remember all that came to present today.
- Privately view your speaker's notes by adding `?presentme=true` to the presentation's html:
  - Example: `mypresentation.vt.html?presentme=true`
</div>


## Highlighting Portion of Code for audience! 

Use `h` to highlight portions of the code for the audience to follow better.

```{r,echo=TRUE}
x <- 10
y <- x * 2
```

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
mcar <- mean(cars$speed)
```

### Using calculated values in the slides.

The mean of the the Speed column is `r mcar`.

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Equations

$$
s^2 = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}
$$

## Creating Tables

Col1       Col2              Col3
------    ----------    ---------
January    Free          Day
February   Reel          Fish
March      Hotness       Cold^[Very]
------    ----------    ---------

Table: My Dataset

