---
title: "Slides in the classroom"
author: "Put your name here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  powerpoint_presentation:
    reference_doc: refer.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3


## Statistics to compute

1. Mean
1. Standard deviation
1. Variance
1. Range
1. Max and Min

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
mcar <- mean(cars$speed)
```

### Using calculated values in the slides.

The mean of the the Speed column is `r mcar`.

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Equations

$$
s^2 = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}
$$

## Equations II

### Create an aligned equation environment
\begin{align}
s^2 & = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}\\
s^2 & = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}\\
s^2 & = \frac{\sum\limits_{i =1}^N (x_i - \bar{x})^2}{N - 1}
\end{align}

\structure{Answers}
Rather easy to create these


## Creating Tables

Col1       Col2              Col3
------    ----------    ---------
January    Free          Day
February   Reel          Fish
March      Hotness       Cold^[Very]
------    ----------    ---------

Table: My Dataset

Included a footnote here... 

\structure{Issue}
- Tables and images appear on separate slides.

## {.plain}

### Plain slide. 

Great for full page graphics etc.


